Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-09-11 arxiv/proof_main.tex

\noindent\textbf{Defining the resolvents.} For our purpose, we introduce a convenient self-adjoint linearization trick,

@@

 We will consistently use the latin letters $i,j\in\sI_{0}$, greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$, and $\fa,\fb,\mathfrak c\in \cal I$. Correspondingly, the indices of the matrices $Z_1$ and $Z_2$ are labelled as

@@

With Schur complement formula, we can check that

@@

 where we abbreviated $W:=n^{-1/2}(\Lambda U^\top Z_1^\top, V^\top Z_2^\top)$. This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block. On the other hand, $G(z)$ is a little  easier to use than $\cal G(z)$, and obviously contains more information.

@@

\medskip
\noindent{\bf Deriving the bias and variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
\be\label{rewrite X as R} (X_1^\top X_1+X_2^\top X_2)^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
When $z=0$, it is easy to check that equation \eqref{selfomega_a} can be reduced to \eqref{eq_a12extra}, which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$. Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$. Together with equation \eqref{rewrite X as R} and $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}, we can obtain equation \eqref{lem_cov_shift_eq} in the large $n$ limit.

>>>>

\noindent\textbf{Defining the resolvents.} For our purpose, we introduce a convenient \alert{self-adjoint linearization trick}\HZ{what does this trick mean? use less technical words},

@@

 We will consistently use the latin letters $i,j\in\sI_{0}$, greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$, and $\fa,\fb,\mathfrak c\in \cal I$ \HZ{This $\fa, \fb$ notation is ugly. Why not just use $a,b$?}. Correspondingly, the indices of the matrices $Z_1$ and $Z_2$ are labelled as

@@

With Schur complement formula, we can check that \HZ{Has $G(z)$ been defined before?}

@@

 where we abbreviated $W:=n^{-1/2}(\Lambda U^\top Z_1^\top, V^\top Z_2^\top)$. \HZ{$W$ is overloaded with the output layers} This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block. On the other hand, $G(z)$ is a little  easier to use than $\cal G(z)$, and obviously contains more information.

@@

\medskip
\noindent{\bf Deriving the bias and variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
\be\label{rewrite X as R} (X_1^\top X_1+X_2^\top X_2)^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
When $z=0$, it is easy to check that equation \eqref{selfomega_a} can be reduced to \eqref{eq_a12extra}, which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$. Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$. \alert{Together with equation \eqref{rewrite X as R} and $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}, we can obtain equation \eqref{lem_cov_shift_eq} in the large $n$ limit.}\HZ{I do not understand this sentence.}
